%-------------------------
% Resume in Latex
% Author: Sourabh Bajaj, modified by Jerred Shepherd
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jerred Shepherd} & Email: \href{mailto:root@sjer.red}{root@sjer.red}\\
  \href{https://sjer.red}{https://sjer.red} & GitHub: \href{https://github.com/shepherdjerred}{https://github.com/shepherdjerred}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Remote}
      {Master of Science in Computer Science}{August 2022 -- Present}
    \resumeSubheading
      {Harding University}{Searcy, AR}
      {Bachelor of Science in Software Development}{August 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Package Manager at Posit Software, PBC (formerly RStudio, PBC)}{Remote}
      {Software Engineer}{September 2021 - Present}
      \resumeItemListStart
        \resumeItem{Frontend rewrite and partial redesign}{Led and implemented a successful rewrite of Package Manager's frontend from Webpack/Vue 2/JavaScript to Vite/Vue 3/TypeScript. Halved the number of third-party dependencies. Decreased the size of the frontend by 80\%. Implemented request caching with TanStack query and runtime typechecking with Zod. Implemented a partial redesign of the interface to make the product more intuitive for first-time users. Implemented best practices such as automated linters, formatters, deploy previews, dependency updates, and tools for a shorter development cycle.}
        \resumeItem{Automated end-to-end testing}{Designed and implemented a framework in Go using Docker for unified testing Package Manager's CLI, backend, frontend, and documentation. This replaced a plethora of tests written in bash/BATS and Python/Selenium. The framework shortened development cycles which allowed for developers to quickly verify their changes locally instead of pushing and waiting on CI.}
        \resumeItem{Secure bootstraping feature}{Designed and implemented a feature to securely configure Package Manager over an insecure channel using public key cryptography.}
      \resumeItemListEnd

    \resumeSubheading
      {Systems Manager at Amazon Web Services}{Seattle, WA}
      {Software Development Engineer}{July 2019 - August 2021}
      \resumeItemListStart
        \resumeItem{\href{https://aws.amazon.com/about-aws/whats-new/2020/05/aws-systems-manager-now-supports-resource-groups-as-targets-for-state-manager/}{State Manager resource groups feature}}
          {Designed, implemented, tested, and deployed a feature which added support for resource group targets to AWS Systems Manager's desired state configuration service.}
        \resumeItem{Developer productivity improvements}{Developed several productivity tools for use by the State Manager team which led to a significant time savings when developing and deploying code including a notification service for CI/CD events, a service operations report generator, and an infrastructure CLI toolkit.}
        \resumeItem{Intern mentorship}{Mentored an intern during their twelve week internship who was ultimately offered a full-time position. Identified a project and scoped the requirements for the intern. Helped the intern during their onboarding, design, and the development of their project which was deployed to production.}
        \resumeItem{Front end for \href{https://docs.aws.amazon.com/systems-manager/latest/userguide/change-manager.html}{AWS Change Manager}}{Implemented the front-end for AWS Change Manager using React and TypeScript.}
        \resumeItem{Service fleet optimization}
          {Identified and implemented ideal server hardware configuration for team's software stack. Updated service dependencies and language runtimes. These improvements led to a 66\% reduction in server infrastructure cost.}
        \resumeItem{Infrastructure improvements}{Significantly reduced the time to build a new AWS region for the State Manager service. Identified and implemented process improvements which led to a drastic reduction in operational work.}
        \resumeItemListEnd

    \resumeSubheading
      {Systems Manager at Amazon Web Services (Internship)}{Seattle, WA}
      {Software Development Engineer Intern}{May 2018 - July 2018}
      \resumeItemListStart
        \resumeItem{\href{https://aws.amazon.com/about-aws/whats-new/2019/02/aws-systems-manager-state-manager-enables-document-sharing-across-accounts/}{State Manager document sharing}}
          {Designed, implemented, tested, and deployed a feature which adds cross-account document sharing for AWS Systems Manager's desired state configuration  service.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/shepherdjerred/homelab}{Kubernetes Homelab}}{A K3s cluster running on a NAS in my home. Managed with cdk8s and ArgoCD. I've written about the technical details on \href{TODO}{my blog}}
    \resumeSubItem{\href{https://github.com/shepherdjerred/discord-plays-pokemon}{Discord Plays Pokémon}}{Play Pokémon co-operatively with your friends on the Discord social application. Runs entirely in-browser on a GPU-accelerated Docker container with support for running on AWS. Audio and video is streamed via Discord, with game input received through a Discord text channel or a React frontend.}
    \resumeSubItem{\href{https://github.com/harding-capstone/engine}{Castle Casters}}{A cross-platform game and game engine written from scratch in Java 11. Uses OpenGL  for 2D graphics rendering and netty for low-level networking with TCP and UDP sockets. Includes \href{https://github.com/harding-capstone/ai}{an AI} trained with a genetic algorithm and a \href{https://github.com/harding-capstone/logic}{robust implementation} of the \href{https://en.wikipedia.org/wiki/Quoridor}{Quoridor} board game.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
